\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-03-18 paper.qmd
Added interpretation for PBMC3k data

- UMAP representation of PBMC3k data with 15 PCs and parameter choice of n:neighbor:30, min_dist:0.1, metric:cosine (author's suggestion) shows three well-separated clusters. The question we need to answer is: Does this UMAP representation preserve the actual data structure, or is something missing or misidentified or misleading?

@@

- To fit the model, first we need to decide how many number bins should allocate along the x and y axes. To make an initial choice, we use MSE plot.

@@

```{r}
#| echo: false
#| fig-cap: " Model in the 2D space with UMAP (<https://youtu.be/CNXjWZMyh_M>)"
#| label: fig-nldervisPBMCUMAP
#| fig-pos: H

@@

<!--add screen shots of model in high-D-->

- You will see three well-separated clusters in high-D as well which gives evidence that UMAP preserves the global structure. Furthermore, there is non-linearity within the clusters which was not identified by the UMAP, which proves that local structure is not preserved.

- Can we find a better parameter choice for UMAP which preserve the local structure as well?

- To do that, we are going to fit models for different parameter choice and select the one which have the lowest error.

@@

- Selected the one with n:neighbor:5, min_dist:0.99, metric:cosine.

@@

@@

## To draw with AIC
aic_plot_pbmc <- ggplot(mse_df_pbmc, aes(x = num_bins, y = aic
)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = 88, linetype="solid",
                color = "red", size=1, alpha = 0.5) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  #scale_colour_manual(values = c("#377eb8")) +
  ylab("AIC") +
  xlab("total number of bins")
## Effective number of bins along x-axis

mse_plot_pbmc <- ggplot(mse_df_pbmc, aes(x = num_bins,
                                       y = mse
)) +
  geom_point() +
  geom_line() +
   geom_vline(xintercept = 88, linetype="solid",
                color = "red", size=1, alpha = 0.5) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  #scale_colour_manual(values = c("#377eb8")) +
  ylab("MSE") +
  xlab("total number of bins")

```{r}
#| echo: false
#| fig-cap: "Goodness of fit statistics from UMAP applied to training S-curve dataset. What is the effective number of bins in each NLDR technique to create a 2D model? The MSE plot have a steep slope at the beginning, indicating that a smaller number of bins causes a larger amount of error. Then, the slope gradually declines or level off, indicating that a higher number of bins generates a smaller error. Using the elbow method, when the total number of bins is set to 144, the slope of the Mean Squared Error (MSE) plot experiences a sudden and noticeable change, resembling an elbow-like shape. This point indicates that adding less bins does not enough to capture the data structure."
#| label: fig-diagnosticpltPBMC3
##| out-width: 100%
#| fig-pos: H

@@

@@

@@

```{r}
#| echo: false
#| fig-cap: "Model in the 2D space with UMAP (<>)"
#| label: fig-nldervisPBMCUMAP3
#| out-width: 100%
#| fig-pos: H

@@

@@

```{r}
#| echo: false
#| fig-cap: "2D layout from UMAP (n_neighbors = 5, min_dist = 0.99, metric = cosine) applied for PBMC3k dataset (a) colored manually in 2D, (b) colored in high-D"
#| label: fig-nldervisPBMCUMAP3Res
#| out-width: 100%
#| fig-pos: H

@@

@@

- Why I choose this dataset? Because I need show that whatever NLDR technique that we use, our model can capture the non-linear structure within clusters as well.

@@

::: {#fig-mnist1_sc layout-ncol="3"}
![](figures/mnist/sc_1.png){#fig-mnist1_sc1}

>>>>

- UMAP representation of PBMC3k data with 15 PCs and parameter choice of n:neighbor:30, min_dist:0.1, metric:cosine (author's suggestion) shows three well-separated clusters (see @fig-nldervisPBMCUMPview). The question we need to answer is: Does this UMAP representation preserve the actual data structure, or is something missing or misidentified or misleading?

@@

- To fit the model, first we need to decide how many number bins should allocate along the x and y axes. To make an initial choice, we use MSE plot (@fig-diagnosticpltPBMC (b)).

@@

```{r}
#| echo: false
#| fig-cap: "Model in the 2D space overlaid on UMAP data."
#| label: fig-nldervisPBMCUMAP
#| fig-pos: H

@@

- As shown in @fig-nldervisPBMCUMAP, there are three well-separated clusters (according to the model in 2D space).

::: {#fig-pbmc1_sc layout-ncol="3" fig-pos="H"}
![](figures/pbmc3k/sc_1.png){#fig-pbmc1_sc1}

![](figures/pbmc3k/sc_2.png){#fig-pbmc1_sc2}

![](figures/pbmc3k/sc_3.png){#fig-pbmc1_sc3}

Screen shots of the **langevitour** of the PBMC3k data set, shows the model in high-D, a video of the tour animation is available at (<https://youtu.be/Gnhh4hfsbbg>).
:::

- According to @fig-pbmc1_sc (a), the model in high-D space shows two well separated clusters. Also, two clusters are really close to each other (see @fig-pbmc1_sc (b)). Furthermore, there are three clusters shown by the model in 2D actually represented in high-D as well (see @fig-pbmc1_sc (c)). Another important thing to notice from the model in high-D space is that the non-linear continuity structure in two well-separated clusters.

- @fig-pbmc1_sc (c) gives evidence that UMAP preserves the global structure. Furthermore, the non-linearity within the clusters shown in @fig-pbmc1_sc (a) proves that local structure is also preserved but that's not visually shown by th UMAP layout in 2D.

- Can we find a better parameter choice for UMAP which shows this non-linear continuity of the big clusters in 2D space as well?

- To do that, we are going to fit models for different parameter choice and select the one which have the lowest model error in high-D (see @tbl-errordiffcomb).

@@

@@

- Selected the one with n:neighbor:5, min_dist:0.99, metric:cosine (see @fig-nldervisPBMCUMAPview2). As shown in @fig-nldervisPBMCUMAPview2, the two big clusters have non-linear continuity structures, two big clusters are well-separated but close to each other, and the two cluster which exists in the one big cluster are really close to each other (see @fig-nldervisPBMCUMAPview2).

@@

## To draw with AIC
aic_plot_pbmc <- ggplot(mse_df_pbmc, aes(x = num_bins, y = aic
)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = 588, linetype="solid",
                color = "red", size=1, alpha = 0.5) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  #scale_colour_manual(values = c("#377eb8")) +
  ylab("AIC") +
  xlab("total number of bins")
## Effective number of bins along x-axis

mse_plot_pbmc <- ggplot(mse_df_pbmc, aes(x = num_bins,
                                       y = mse
)) +
  geom_point() +
  geom_line() +
   geom_vline(xintercept = 588, linetype="solid",
                color = "red", size=1, alpha = 0.5) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  #scale_colour_manual(values = c("#377eb8")) +
  ylab("MSE") +
  xlab("total number of bins")

```{r}
#| echo: false
#| fig-cap: "Goodness of fit statistics from UMAP applied to training S-curve dataset. What is the effective number of bins in each NLDR technique to create a 2D model? The MSE plot have a steep slope at the beginning, indicating that a smaller number of bins causes a larger amount of error. Then, the slope gradually declines or level off, indicating that a higher number of bins generates a smaller error. Using the elbow method, when the total number of bins is set to 588, the slope of the Mean Squared Error (MSE) plot experiences a sudden and noticeable change, resembling an elbow-like shape. This point indicates that adding less bins does not enough to capture the data structure."
#| label: fig-diagnosticpltPBMC3
##| out-width: 100%
#| fig-pos: H

@@

benchmark_value_rm_lwd <- stats::quantile(df_bin_centroids_pbmc$std_counts, 
                probs = c(0,0.25,0.5,0.75,1), names = FALSE)[2]

df_bin_centroids_low <- df_bin_centroids_pbmc |>
  dplyr::filter(std_counts <= benchmark_value_rm_lwd)

identify_rm_bins <- find_low_dens_hex(df_bin_centroids_all = df_bin_centroids_pbmc, 
                                      num_bins_x = num_bins_x_pbmc, 
                                      df_bin_centroids_low = df_bin_centroids_low)

df_bin_centroids_pbmc <- df_bin_centroids_pbmc |>
  dplyr::filter(!(hexID %in% identify_rm_bins))

@@

## To find the benchmark value
benchmark_pbmc <- find_lg_benchmark(distance_edges = distance_pbmc, distance_col = "distance")
benchmark_pbmc <- 0.08

@@

```{r}
#| echo: false
#| fig-cap: "(a) Model in the 2D space overlaid with UMAP data, and (b) Error occurred by the high-D model for high-D data and the error mapped into 2D NLDR points."
#| label: fig-nldervisPBMCUMAP3
#| out-width: 100%
#| fig-pos: H

@@

- According to @fig-nldervisPBMCUMAP3 (a), the model constructed in 2D space for the new parameter choice of UMAP shows 5 clusters which are really close to each other. The big cluster shows the non-linear continuity structure with two sub clusters. Other three clusters positioned in a structure of non-linearity but really close to each other.

::: {#fig-pbmc2_sc layout-ncol="3" fig-pos="H"}
![](figures/pbmc3k/sc_4.png){#fig-pbmc2_sc1}

![](figures/pbmc3k/sc_5.png){#fig-pbmc2_sc2}

![](figures/pbmc3k/sc_6.png){#fig-pbmc2_sc3}

Screen shots of the **langevitour** of the PBMC3k data set, shows the model in high-D with new parameter choice for UMAP, a video of the tour animation is available at (<https://youtu.be/lc_6-rIuNHI>).
:::

- As shown in @fig-pbmc2_sc, there are 5 clusters, three of them are well-separated but close to each other as seen in @fig-nldervisPBMCUMAP3 (a). Also, other two clusters are really close to each other but separated from the early mentioned three clusters.

- Next, we are going to investigate whether, the clusters we identified in 2D UMAP layout, can also be identified in high-D as well.

- First, I colored the clusters in 2D layout manually. Then, I used spin-and-brush approach with `detour` to color the clusters in high-D.

@@

```{r}
#| echo: false
#| fig-cap: "2D layout from UMAP (n_neighbors = 5, min_dist = 0.99, metric = cosine) applied for PBMC3k dataset (a) colored manually in 2D, (b) colored in high-D."
#| label: fig-nldervisPBMCUMAP3Res
#| out-width: 100%
#| fig-pos: H

@@

- @fig-nldervisPBMCUMAP3Res shows the 2D UMAP layout colored with each method. As shown in @fig-nldervisPBMCUMAP3Res (b) and the confusion matrix,there are some miss-classifications. What is the reason for that?

- For example, the point (ID: 1158) classified as **cluster 3** in 2D UMAP layout, classified as **cluster 6** when doing the colouring in high-D (see @fig-nldervisPBMCUMAP3Res). Why?

::: {#fig-pbmc2_appsc layout-ncol="1" fig-pos="H"}
![](figures/pbmc3k/sc_7.png){#fig-pbmc2_sc7}

Screen shots of app which shows 2D UMAP layout and comparison of distances related to the point classified as **cluster 6** in high-D (ID: 1158) and randomly selected point which is in **cluster 6** (ID: 2291).
:::

- If we compute the distance between these two points, you will see that it preserves the pair-wise distance (see @fig-pbmc2_appsc), which give us a evidence that even though the point 1158, classified as **cluster 3** in 2D layout, actually should be in **cluster 6**. This also evident that some misleading can happens with UMAP.

::: {#fig-pbmc2_appsc1 layout-ncol="1" fig-pos="H"}
![](figures/pbmc3k/sc_8.png){#fig-pbmc2_sc8}

Screen shots of app which shows 2D UMAP layout and comparison of distances related to the point classified as **cluster 5** in high-D (ID: 3) and randomly selected point which is in **cluster 5** (ID: 2198).
:::

- For another example, if we compute the distance between these two points, you will see that it preserves the pair-wise distance (see @fig-pbmc2_appsc1), which give us a evidence that even though the point 3, classified as **cluster 4** in 2D layout, actually should be in **cluster 5**. This also evident that some misleading can happens with UMAP.

df_all_pbmc <- dplyr::bind_cols(training_data_pbmc, umap_data_with_hb_id_pbmc)

df_all_pbmc <- inner_join(df_all_pbmc, detour_results8, by = c("ID" = "ID"))

### Define type column
df <- df_all_pbmc |>
  dplyr::select(tidyselect::starts_with("PC_"), result2_class_label) |>
  dplyr::rename("type" = "result2_class_label") ## original dataset

df_b <- df_bin_pbmc |>
  dplyr::filter(hb_id %in% df_bin_centroids_pbmc$hexID) |>
  dplyr::mutate(type = "model") ## Data with summarized mean

## Reorder the rows of df_b according to the hexID order in df_b_with_center_data
df_b <- df_b[match(df_bin_centroids_pbmc$hexID, df_b$hb_id),] |>
  dplyr::select(-hb_id)

df_exe <- dplyr::bind_rows(df_b, df)

 ## Set the maximum difference as the criteria
distance_df_small_edges <- distance_pbmc |>
  dplyr::filter(distance < benchmark_pbmc)
## Since erase brushing is considerd.

# langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
#                          lineFrom = distance_df_small_edges$from,
#                            lineTo = distance_df_small_edges$to,
#                          group = df_exe$type, pointSize = 3,
#                          levelColors = c("#d82cd3", "#49df20", "#619cff", "#000000", "#df2020", "#ffbd61", "#33a02c"))

@@

- Why I choose this data set? Because I need show that whatever NLDR technique that we use, our model can capture the non-linear structure within clusters as well.

@@

::: {#fig-mnist1_sc layout-ncol="3" fig-pos="H"}
![](figures/mnist/sc_1.png){#fig-mnist1_sc1}

### 2024-03-18 paper.tex
Added interpretation for PBMC3k data

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, breakable, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

\begin{itemize}
\tightlist
\item
  UMAP representation of PBMC3k data with 15 PCs and parameter choice of
  n:neighbor:30, min\_dist:0.1, metric:cosine (author's suggestion)
  shows three well-separated clusters. The question we need to answer
  is: Does this UMAP representation preserve the actual data structure,
  or is something missing or misidentified or misleading?
\end{itemize}

@@

\begin{itemize}
\item
  To investigate this, we are going to visualise the model in the data
  space, which means that the model generated from UMAP is visualised in
  high-D with original data.
\item
  To fit the model, first we need to decide how many number bins should
  allocate along the x and y axes. To make an initial choice, we use MSE
  plot.
\end{itemize}

@@

\caption{\label{fig-nldervisPBMCUMAP}Model in the 2D space with UMAP
(\url{https://youtu.be/CNXjWZMyh_M})}

@@

\begin{itemize}
\item
  You will see three well-separated clusters in high-D as well which
  gives evidence that UMAP preserves the global structure. Furthermore,
  there is non-linearity within the clusters which was not identified by
  the UMAP, which proves that local structure is not preserved.
\item
  Can we find a better parameter choice for UMAP which preserve the
  local structure as well?
\item
  To do that, we are going to fit models for different parameter choice
  and select the one which have the lowest error.
\end{itemize}

@@

\begin{itemize}
\item
  Selected the one with n:neighbor:5, min\_dist:0.99, metric:cosine.
\item
  Now, we are going to fit the model for the new parameter choice.
\end{itemize}

@@

@@

\caption{\label{fig-diagnosticpltPBMC3}Goodness of fit statistics from
UMAP applied to training S-curve dataset. What is the effective number
of bins in each NLDR technique to create a 2D model? The MSE plot have a
steep slope at the beginning, indicating that a smaller number of bins
causes a larger amount of error. Then, the slope gradually declines or
level off, indicating that a higher number of bins generates a smaller
error. Using the elbow method, when the total number of bins is set to
144, the slope of the Mean Squared Error (MSE) plot experiences a sudden
and noticeable change, resembling an elbow-like shape. This point
indicates that adding less bins does not enough to capture the data
structure.}

@@

\caption{\label{fig-nldervisPBMCUMAP3}Model in the 2D space with UMAP
(\textless\textgreater)}

@@

@@

\caption{\label{fig-nldervisPBMCUMAP3Res}2D layout from UMAP
(n\_neighbors = 5, min\_dist = 0.99, metric = cosine) applied for PBMC3k
dataset (a) colored manually in 2D, (b) colored in high-D}

@@

@@

\begin{itemize}
\item
  Why I choose this dataset? Because I need show that whatever NLDR
  technique that we use, our model can capture the non-linear structure
  within clusters as well.
\item
  Digit 1 (7877 images only)
\end{itemize}

@@

\includegraphics{paper_files/figure-pdf/unnamed-chunk-84-1.pdf}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, frame hidden, sharp corners, breakable]}{\end{tcolorbox}}\fi

@@

\begin{itemize}
\tightlist
\item
  UMAP representation of PBMC3k data with 15 PCs and parameter choice of
  n:neighbor:30, min\_dist:0.1, metric:cosine (author's suggestion)
  shows three well-separated clusters (see
  Figure~\ref{fig-nldervisPBMCUMPview}). The question we need to answer
  is: Does this UMAP representation preserve the actual data structure,
  or is something missing or misidentified or misleading?
\end{itemize}

@@

\begin{itemize}
\item
  To investigate this, we are going to visualise the model in the data
  space, which means that the model generated from UMAP is visualised in
  high-D with original data.
\item
  To fit the model, first we need to decide how many number bins should
  allocate along the x and y axes. To make an initial choice, we use MSE
  plot (Figure~\ref{fig-diagnosticpltPBMC} (b)).
\end{itemize}

@@

\caption{\label{fig-nldervisPBMCUMAP}Model in the 2D space overlaid on
UMAP data.}

@@

\begin{itemize}
\tightlist
\item
  As shown in Figure~\ref{fig-nldervisPBMCUMAP}, there are three
  well-separated clusters (according to the model in 2D space).
\end{itemize}

\includegraphics{figures/pbmc3k/sc_1.png}

\subcaption{\label{fig-pbmc1_sc1}}
\end{minipage}%
%
\begin{minipage}[t]{0.33\linewidth}

\includegraphics{figures/pbmc3k/sc_2.png}

\subcaption{\label{fig-pbmc1_sc2}}
\end{minipage}%
%
\begin{minipage}[t]{0.33\linewidth}

\includegraphics{figures/pbmc3k/sc_3.png}

\subcaption{\label{fig-pbmc1_sc3}}
\end{minipage}%

\caption{\label{fig-pbmc1_sc}Screen shots of the \textbf{langevitour} of
the PBMC3k data set, shows the model in high-D, a video of the tour
animation is available at (\url{https://youtu.be/Gnhh4hfsbbg}).}

\begin{itemize}
\item
  According to Figure~\ref{fig-pbmc1_sc} (a), the model in high-D space
  shows two well separated clusters. Also, two clusters are really close
  to each other (see Figure~\ref{fig-pbmc1_sc} (b)). Furthermore, there
  are three clusters shown by the model in 2D actually represented in
  high-D as well (see Figure~\ref{fig-pbmc1_sc} (c)). Another important
  thing to notice from the model in high-D space is that the non-linear
  continuity structure in two well-separated clusters.
\item
  Figure~\ref{fig-pbmc1_sc} (c) gives evidence that UMAP preserves the
  global structure. Furthermore, the non-linearity within the clusters
  shown in Figure~\ref{fig-pbmc1_sc} (a) proves that local structure is
  also preserved but that's not visually shown by th UMAP layout in 2D.
\item
  Can we find a better parameter choice for UMAP which shows this
  non-linear continuity of the big clusters in 2D space as well?
\item
  To do that, we are going to fit models for different parameter choice
  and select the one which have the lowest model error in high-D (see
  \textbf{?@tbl-errordiffcomb}).
\end{itemize}

@@

@@

\begin{itemize}
\item
  Selected the one with n:neighbor:5, min\_dist:0.99, metric:cosine (see
  Figure~\ref{fig-nldervisPBMCUMAPview2}). As shown in
  Figure~\ref{fig-nldervisPBMCUMAPview2}, the two big clusters have
  non-linear continuity structures, two big clusters are well-separated
  but close to each other, and the two cluster which exists in the one
  big cluster are really close to each other (see
  Figure~\ref{fig-nldervisPBMCUMAPview2}).
\item
  Now, we are going to fit the model for the new parameter choice.
\end{itemize}

@@

\caption{\label{fig-diagnosticpltPBMC3}Goodness of fit statistics from
UMAP applied to training S-curve dataset. What is the effective number
of bins in each NLDR technique to create a 2D model? The MSE plot have a
steep slope at the beginning, indicating that a smaller number of bins
causes a larger amount of error. Then, the slope gradually declines or
level off, indicating that a higher number of bins generates a smaller
error. Using the elbow method, when the total number of bins is set to
588, the slope of the Mean Squared Error (MSE) plot experiences a sudden
and noticeable change, resembling an elbow-like shape. This point
indicates that adding less bins does not enough to capture the data
structure.}

@@

\caption{\label{fig-nldervisPBMCUMAP3}(a) Model in the 2D space overlaid
with UMAP data, and (b) Error occurred by the high-D model for high-D
data and the error mapped into 2D NLDR points.}

@@

\begin{itemize}
\tightlist
\item
  According to Figure~\ref{fig-nldervisPBMCUMAP3} (a), the model
  constructed in 2D space for the new parameter choice of UMAP shows 5
  clusters which are really close to each other. The big cluster shows
  the non-linear continuity structure with two sub clusters. Other three
  clusters positioned in a structure of non-linearity but really close
  to each other.
\end{itemize}

\includegraphics{figures/pbmc3k/sc_4.png}

\subcaption{\label{fig-pbmc2_sc1}}
\end{minipage}%
%
\begin{minipage}[t]{0.33\linewidth}

\includegraphics{figures/pbmc3k/sc_5.png}

\subcaption{\label{fig-pbmc2_sc2}}
\end{minipage}%
%
\begin{minipage}[t]{0.33\linewidth}

\includegraphics{figures/pbmc3k/sc_6.png}

\subcaption{\label{fig-pbmc2_sc3}}
\end{minipage}%

\caption{\label{fig-pbmc2_sc}Screen shots of the \textbf{langevitour} of
the PBMC3k data set, shows the model in high-D with new parameter choice
for UMAP, a video of the tour animation is available at
(\url{https://youtu.be/lc_6-rIuNHI}).}

\begin{itemize}
\item
  As shown in Figure~\ref{fig-pbmc2_sc}, there are 5 clusters, three of
  them are well-separated but close to each other as seen in
  Figure~\ref{fig-nldervisPBMCUMAP3} (a). Also, other two clusters are
  really close to each other but separated from the early mentioned
  three clusters.
\item
  Next, we are going to investigate whether, the clusters we identified
  in 2D UMAP layout, can also be identified in high-D as well.
\item
  First, I colored the clusters in 2D layout manually. Then, I used
  spin-and-brush approach with \texttt{detour} to color the clusters in
  high-D.
\end{itemize}

@@

\caption{\label{fig-nldervisPBMCUMAP3Res}2D layout from UMAP
(n\_neighbors = 5, min\_dist = 0.99, metric = cosine) applied for PBMC3k
dataset (a) colored manually in 2D, (b) colored in high-D.}

@@

\begin{itemize}
\item
  Figure~\ref{fig-nldervisPBMCUMAP3Res} shows the 2D UMAP layout colored
  with each method. As shown in Figure~\ref{fig-nldervisPBMCUMAP3Res}
  (b) and the confusion matrix,there are some miss-classifications. What
  is the reason for that?
\item
  For example, the point (ID: 1158) classified as \textbf{cluster 3} in
  2D UMAP layout, classified as \textbf{cluster 6} when doing the
  colouring in high-D (see Figure~\ref{fig-nldervisPBMCUMAP3Res}). Why?
\end{itemize}

\begin{minipage}[t]{\linewidth}

\includegraphics{figures/pbmc3k/sc_7.png}

\subcaption{\label{fig-pbmc2_sc7}}
\end{minipage}%

\caption{\label{fig-pbmc2_appsc}Screen shots of app which shows 2D UMAP
layout and comparison of distances related to the point classified as
\textbf{cluster 6} in high-D (ID: 1158) and randomly selected point
which is in \textbf{cluster 6} (ID: 2291).}

\begin{itemize}
\tightlist
\item
  If we compute the distance between these two points, you will see that
  it preserves the pair-wise distance (see
  Figure~\ref{fig-pbmc2_appsc}), which give us a evidence that even
  though the point 1158, classified as \textbf{cluster 3} in 2D layout,
  actually should be in \textbf{cluster 6}. This also evident that some
  misleading can happens with UMAP.
\end{itemize}

\begin{minipage}[t]{\linewidth}

\includegraphics{figures/pbmc3k/sc_8.png}

\subcaption{\label{fig-pbmc2_sc8}}
\end{minipage}%

\caption{\label{fig-pbmc2_appsc1}Screen shots of app which shows 2D UMAP
layout and comparison of distances related to the point classified as
\textbf{cluster 5} in high-D (ID: 3) and randomly selected point which
is in \textbf{cluster 5} (ID: 2198).}

\begin{itemize}
\tightlist
\item
  For another example, if we compute the distance between these two
  points, you will see that it preserves the pair-wise distance (see
  Figure~\ref{fig-pbmc2_appsc1}), which give us a evidence that even
  though the point 3, classified as \textbf{cluster 4} in 2D layout,
  actually should be in \textbf{cluster 5}. This also evident that some
  misleading can happens with UMAP.
\end{itemize}

@@

\begin{itemize}
\item
  Why I choose this data set? Because I need show that whatever NLDR
  technique that we use, our model can capture the non-linear structure
  within clusters as well.
\item
  Digit 1 (7877 images only)
\end{itemize}

@@

\includegraphics{paper_files/figure-pdf/unnamed-chunk-85-1.pdf}
